Combinatorial interpretations of holonomic recurrences

### 2021-08-27 article/main.tex
Add diff support
Create overview

% \date{Kraków, 19 maja 2021}

@@

We also try to find combinatorial interpretation of holonomic recurrence for trees of lambda terms in de Bruijn notation.

@@

@@

\begin{thebibliography}{9}
    \bibitem{gfun}
    Bruno Salvy, Paul Zimmermann,
    \textit{GFUN : a maple package for the manipulation of generating and holonomic functions in one variable}
    [Research Report] RT-0143, INRIA. 1992, pp.14. ffinria-00070025f

>>>>

\date{\today}

@@

We also try to find a combinatorial interpretation of the holonomic recurrence for trees of lambda terms in the de Bruijn notation.

@@

\section{Overview}%
Initial inspiration for the thesis came from \textit{A natural counting of lambda terms}\cite{zigzag} publication, which shows bijection between seemingly different tree structures, which are lambda trees, black-white trees nad zigzag free trees.
\todo{Finish the overview section}

@@

\begin{thebibliography}{9}
    \bibitem{zigzag}
    Maciej Bendkowski, Katarzyna Grygiel, Pierre Lescanne, Marek Zaionc,
    \textit{A natural counting of lambda terms},
    2016

    \bibitem{gfun}
    Bruno Salvy, Paul Zimmermann,
    \textit{GFUN : a maple package for the manipulation of generating and holonomic functions in one variable},
    [Research Report] RT-0143, INRIA. 1992, pp.14. ffinria-00070025f
